---
title: "simple_use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simple_use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(multimodalCT)
```


## Minimal Example

We have $z$ neutral traits, specifc for each community, with no sexual biases and all transmitted from pre migration horizontal copying

```{r}
z=4
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$pre[,"h"]=1
neutraltraitsParam$s=rep(.5,z)
traitsid=paste0("t",1:z)
```


To simplify we define $K=z$ communities, 1 communities is of farmer, the other are of hunter gatherer , with 150 individual per community, 150 will also be the Fission Threshold (ie community starts at maximum pop size).

Communities are defined by thee aspect:
1. presence absence of adaptive traits and number of such traits
2. position on the map
3. size


Thes three aspc can be initialised as follow:

### The traits:
```{r initparam,out.width="40%"}
km=1
ki=z-1
traits=initAdaptiveTraits(ki=ki,km=km,n=3) # this generate a table for 3 adaptive traits, with ki communities of full hunter-gathere and km of farmers
```


The position:

```{r}
G=2 #limits/numer of row & column of the world grid
coordinates=random2Dgrid(K=ki+km,Gx=G) #random coordinated on the grid
```

We use these to generate the communities, the size for now being fixed at 150

```{r}
initcomus=initialiseCommunities(traits=traits,coordinates=coordinates,G=G,sizes=150,plot=T)
text(initcomus$coordinates[,1],initcomus$coordinates[,2],labels=1:nrow(initcomus$coordinates))
cols=c("#E41A1C","#377EB8","#4DAF4A","#984EA3")
plot(initcomus$coordinates[,1],initcomus$coordinates[,2],bg=cols,pch=21,cex=20)
text(initcomus$coordinates[,1],initcomus$coordinates[,2],labels=1:nrow(initcomus$coordinates))
```

We then initialise a random population based on these communities:
```{r randompop}
communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(n=sum(initcomus$size),age="random",community = communities),initNeutralTraits(sum(initcomus$size),z))
```


We run a first simulation to have a proper age and family structure 

```{r runburnin,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=100
burnin=modelVector(
   K=ki, m=1, b=0.2, r=0, rho=0, d=0.01, maturity=18, endrepro=65, 
   population=population, 
   comus=initcomus, 
   tstep=tstep, 
   tp=initNeutralTraitsPathways(z = z) , #we recreate a temporary neutral trait table with no neutral transmission
   age.threshold=20, 
   out=c("finalpop","finalcomus"),   #we only want the final population
   logging=c("done"),ma=1,traitsid=paste0("t",1:z),F_Th = 150
)
```

We use the output of theis simulation as our starting points

```{r getburnin,results='asis'}
population=burnin$population
initcomus$size=burnin$finalcomus$size
```

There is a bit of redundancy here as `burnin$finalcomus$size` is (and should always be) the same than `table(population[,"community"])`

We need now to reset the neutral traits and set them as unique in each population

```{r setuppopulation}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
```

We can also reset ids to start at one and have more readable results:


```{r resetids}
population[population[,"cid"]!= -1 ,"cid"] = as.numeric(as.factor(as.character(population[population[,"cid"]!= -1 ,"cid"])))
population[,"fid"] = as.numeric(as.factor(as.character(population[ ,"fid"])))
ids = as.numeric(as.factor(as.character(population[ ,"id"])))
names(ids)=population[,"id"]
population[,"id"] = as.numeric(as.factor(as.character(population[ ,"id"])))
population[,"partner"]=as.numeric(ids[as.character(population[,"partner"])])
population[is.na(population[,"partner"]),"partner"]=-1
```

(this is done in `data-raw/population.R` to generate the dataset `population` available from the package)


We can now run a proper simulation:


```{r runpropersimu}
tstep=500
simuTest=modelVector(
    K=ki, m=1, b=0.2, r=0.01, rho=0, d=0.01, 
    maturity=18, endrepro=65, 
    population=population, 
    comus=initcomus, 
    tstep=tstep, 
    tp=neutraltraitsParam,
    age.threshold=20, 
    out=c("finalpop","finalcomus","traitsumary","popsize"), #this time we keep track of more things
    logging=c("done"),
    beta=0,
    ma=1,traitsid=paste0("t",1:z),F_Th = 150
)
```


The choice of parameter should ensure a stable population:

```{r followpopsize}
plot(simuTest$popsize,type="l",ylim=c(300,650),lwd=5,xlab="time",ylab="number of individual")
```

The parameter `out` define what's available as outcome, and multiple things are available. `finalpop` tells the model to return the population at the final time step. Using that we can look at the distribution of traits at the end:

```{r finaldistrib,fig.show="hold"}

knitr::kable(aggregate(simuTest$population[,traitsid],by=list(simuTest$population[,"community"]),FUN=getRatio))

barplot(as.matrix(aggregate(simuTest$population[,traitsid],by=list(simuTest$population[,"community"]),FUN=getRatio)[,-1]),beside=T,col=cols,main="percentage of population with traits")
barplot(table(simuTest$population[,"community"]),col=cols,main="community size")

```

```{r}

simuTest$finalcomus

```


We can track the frequencie of each traits using "traitsumary"

```{r runsimu-pre,warnings=FALSE,results=FALSE,results='hold'}


```


replicate experiments

```{r,eval=F}
tstep=100
repli=50
neutraltraitsParam$s=c(.5,.5,.5,.5)
rhodep=lapply(c(0,1),function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           allinlaw=replicate(repli,
                              {
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           allposthoriz=replicate(repli,{
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                      pop=quickV$population
                                      sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)


           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           allprehoriz=replicate(repli,{
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

           list(allinlaw=allinlaw,allposthoriz=allposthoriz,allprehoriz=allprehoriz)
}
)

```
