```{r}
devtools::load_all(".")

N=300
Th=400 #fission threshold
ki <- 2
km <- 1
K  <-  ki+km
m=1 #proba marriage
b=.2 #HG birth rate
r=.05 #farmer scale param
rho=.5 #marriage rule
d=0.001
maturity=0
endrepro=20

a=initAdaptiveTraits(ki=ki,km=km)
z=4 #number of neutral traits
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)

ip=1:N
names(ip)=ip
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(endrepro-5,1), community=sample.int(K,1), sex=sample(c("F","M"),1), repro=FALSE, partner=-1))
                                      population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))

pos=random2Dgrid(K=K,Gx=2)
initcomus=initialiseCommunities(traits=a,coordinates=pos,G=2,plot=T)
size=table(sapply(population,"[[","community"))
initcomus$size=size
plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))


tstep=200

quick=modelVector( K =K, m=m, b=b, r=r, rho=rho, d=d, maturity=maturity, endrepro=endrepro, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam, logging=c("na"),ma=1,F_Th=NULL)


plot(quick$popsize)

tstep=50
maturity=18
endrepro=60
m=.2
quick=modelOOstyle( K =K, m=m, b=b, r=r, rho=rho, d=d, maturity=maturity, endrepro=endrepro, population=population,comus=initcomus, tstep=tstep, neutraltraitsParam=neutraltraitsParam, logging=c("na"),ma=1)
plot(quick$popsize)
sumcomu=sapply(quick$popsum,"[[","community")
plot(1:tstep,ylim=range(sumcomu),type="n",ylab="pop size",,xlab="time")
lapply(1:K,function(k) lines(sumcomu[k,],col=mean(initcomus$adaptivetraits[k,])+1,lwd=3) )
```

Having only one community with only one kind of traits (all 0 or all 1), maturity and compare to
$$ N_t=N_{t-1}+\Sigma(poiss(b+r \times a,N_{t-1}))-N_{(t-1)} \times d $$ with a=0 for I, 1 for M

```{r}
library(parallel)
m=1
b=0.2
r=0.05
tstep=300
d=0.001
N=200
ip=1:N
names(ip)=ip
z=4 #number of neutral traits
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(65,1), community=1, sex=sample(c("F","M"),1), repro=FALSE, partner=-1))

pos=random2Dgrid(K=1,Gx=100)

tstep=30
for(mature_adjust in c(1,60)){

    cl=makeCluster(10,"FORK")
    tentriesOnlyF=parLapply(cl,1:10,function(i){set.seed(as.numeric(Sys.time())+i);modelOOstyle(m=m, b=b, r=r,  d=d, maturity=0, endrepro=10000, logging="time", population=population, comus=initialiseCommunities(traits=initAdaptiveTraits(ki=0,km=1),coordinates=pos) , tstep=tstep, neutraltraitsParam=neutraltraitsParam,ma=mature_adjust)})

    tentriesOnlyHG=parLapply(cl,1:10,function(i){set.seed(as.numeric(Sys.time())+i);modelOOstyle(m=m, b=b, r=r,  d=d, maturity=0, endrepro=10000, logging="time", population=population, comus=initialiseCommunities(traits=initAdaptiveTraits(ki=1,km=0),coordinates=pos) , tstep=tstep, neutraltraitsParam=neutraltraitsParam,ma=mature_adjust)})

    stopCluster(cl)

    xyr=range(sapply(tentriesOnlyF,"[[","popsize"), sapply(tentriesOnlyHG,"[[","popsize"))
    plot(1:tstep,ylim=xyr,type="n",log="y",ylab="pop size",,xlab="time")
    lapply(tentriesOnlyF,function(res) lines(res$popsize,col=2,lwd=3) )
    lapply(tentriesOnlyHG,function(res) lines(res$popsize,col=1,lwd=3) )



    ## Demographic model only
    for(i in 1:100){
        hg=vector("numeric",tstep/mature_adjust)
        fa=vector("numeric",tstep/mature_adjust)
        fa[1]=N
        hg[1]=N

        for(i in 2:max(3,tstep/mature_adjust)){
            hg[i]=hg[i-1]+sum(rpois(hg[i-1],b+r*sum(c(0,0,0))))-hg[i-1]*d
            fa[i]=fa[i-1]+sum(rpois(fa[i-1],b+r*sum(c(1,1,1))))-fa[i-1]*d
        }
        #plot(1,1,type="n",ylim=range(hg,fa),xlim=c(0,dur))
        lines(c(1,2:(length(fa))*(mature_adjust)),fa,col=2,lty=2,lwd=1)
        lines(c(1,2:(length(hg))*(mature_adjust)),hg,col=1,lty=2,lwd=1)
    }
    legend("bottomright",legend=c(expression(N[t]==N[t-1]+Sigma(poiss(b,N[t-1]))-N[t-1]*d),expression(N[t]==N[t-1]+Sigma(poiss(b+r,N[t-1]))-N[t-1]*d),"model 1 community HG","model 1 communit F"),lty=c(2,2,1,1),col=c(1,2,1,2),cex=.8)
}


popvec=listToVec(population)
for(mature_adjust in c(1,60)){

    cl=makeCluster(10,"FORK")
    tentriesOnlyF=parLapply(cl,1:10,function(i){set.seed(as.numeric(Sys.time())+i);modelVector(m=m, b=b, r=r,  d=d, maturity=0, endrepro=10000, logging="time", population=popvec,comus=initialiseCommunities(traits=initAdaptiveTraits(ki=0,km=1),coordinates=pos) , tstep=tstep, neutraltraitsParam=neutraltraitsParam,ma=mature_adjust)})

    tentriesOnlyHG=parLapply(cl,1:10,function(i){set.seed(as.numeric(Sys.time())+i);modelVector(m=m, b=b, r=r,  d=d, maturity=0, endrepro=10000, logging="time", population=popveccomus=initialiseCommunities(traits=initAdaptiveTraits(ki=1,km=0),coordinates=pos) , tstep=tstep, neutraltraitsParam=neutraltraitsParam,ma=mature_adjust)})

    stopCluster(cl)

    xyr=range(sapply(tentriesOnlyF,"[[","popsize"), sapply(tentriesOnlyHG,"[[","popsize"))
    plot(1:tstep,ylim=xyr,type="n",log="y",ylab="pop size",,xlab="time")
    lapply(tentriesOnlyF,function(res) lines(res$popsize,col=2,lwd=3) )
    lapply(tentriesOnlyHG,function(res) lines(res$popsize,col=1,lwd=3) )



    ## Demographic model only
    for(i in 1:100){
        hg=vector("numeric",tstep/mature_adjust)
        fa=vector("numeric",tstep/mature_adjust)
        fa[1]=N
        hg[1]=N

        for(i in 2:max(3,tstep/mature_adjust)){
            hg[i]=hg[i-1]+sum(rpois(hg[i-1],b+r*sum(c(0,0,0))))-hg[i-1]*d
            fa[i]=fa[i-1]+sum(rpois(fa[i-1],b+r*sum(c(1,1,1))))-fa[i-1]*d
        }
        #plot(1,1,type="n",ylim=range(hg,fa),xlim=c(0,dur))
        lines(c(1,2:(length(fa))*(mature_adjust)),fa,col=2,lty=2,lwd=1)
        lines(c(1,2:(length(hg))*(mature_adjust)),hg,col=1,lty=2,lwd=1)
    }
    legend("bottomright",legend=c(expression(N[t]==N[t-1]+Sigma(poiss(b,N[t-1]))-N[t-1]*d),expression(N[t]==N[t-1]+Sigma(poiss(b+r,N[t-1]))-N[t-1]*d),"model 1 community HG","model 1 communit F"),lty=c(2,2,1,1),col=c(1,2,1,2),cex=.8)
}


```


```{r}
m=1
b=0.2
r=0.05
tstep=300
d=0.001
N=200
ip=1:N
names(ip)=ip
z=4 #number of neutral traits
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(65,1), community=1, sex=sample(c("F","M"),1), repro=FALSE, partner=-1))




neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=2)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=2,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))
quickV=modelVector(K=K, m=1, b=0.1, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z))


alldeath=replicate(100,length(modelVector(K=K, m=1, b=0, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize"),logging=NULL,ma=1,traitsid=paste0("t",1:z))$popsize))

alldeath2=replicate(100,length(modelVector(K=K, m=1, b=0.1, r=0, rho=.5, d=0.04, maturity=18, endrepro=85, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize"),logging=NULL,ma=1,traitsid=paste0("t",1:z))$popsize))
boxplot(alldeath,alldeath2)

modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize"),logging=NULL,ma=1,traitsid=paste0("t",1:z))$births
boxplot(alldeath,alldeath2)

initcomus$occupation[,]=1
testres=modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=800, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize","finalpop"),logging="time",ma=1,traitsid=paste0("t",1:z),F_Th=50)


population=testres$population
rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))
population=resetIds(population)

nrow(population[validCouple(population, maturity=18, endrepro=65),])
multirep=replicate(10,modelVector(K=K, m=1, b=10*0.04, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize","finalpop","repros"),logging="time",ma=1,traitsid=paste0("t",1:z)))

newtestres=modelVector(K=K, m=1, b=0.5, r=0, rho=.5, d=0.043, maturity=18, endrepro=65, population=testres$population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging="time",ma=1,traitsid=paste0("t",1:z))
plot(newtestres$deaths)
par(mfrow=c(3,2))
plot(newtestres$popsize,main="population size")
plot(newtestres$repro,main="number of valid couple")
plot(newtestres$popsize[-1],newtestres$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")
plot(newtestres$popsize[-1],newtestres$repros,xlab="population size",ylab=,main="#parents vs popsize")
plot(newtestres$repros/newtestres$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2)

plot(newtestres$popsize[-1],newtestres$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
for(repil in 1:ncol(multirep)) points(multirep[,repil]$popsize[-1],multirep[,repil]$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")

par(mfrow=c(3,2))
exp=newtestres
plot(exp$popsize,main="population size",xlab="time",ylab="# number individual",log="y",ylim=c(1,10000),type="l",lwd=2)
for(repil in 1:ncol(multirep)) lines(multirep[,repil]$popsize,,main="#death vs popsize",col=repil,lwd=2)
plot(newtestres$repro,main="number of valid couple",type="l",log="y",lwd=2,ylim=c(1,2000))
for(repil in 1:ncol(multirep)) 
lines(multirep[,repil]$repro,main="number of valid couple",col=repil,type="l",lwd=2)
plot(newtestres$popsize[-1],newtestres$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$deaths,xlab="population size",ylab="number of death",main="#death vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$births,xlab="population size",ylab="number of birth",main="#birth vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$repros,xlab="population size",ylab="number parents",main="#parents vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$repros,col=repil)
plot(newtestres$repros/newtestres$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,ylim=c(0,.5))
for(repil in 1:ncol(multirep)) 
lines(multirep[,repil]$repros/multirep[,repil]$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,col=repil)

multirep=sapply(,modelVector(K=K, m=1, b=10*0.04, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize","finalpop","repros"),logging="time",ma=1,traitsid=paste0("t",1:z)))

newtestres=modelVector(K=K, m=1, b=0.5, r=0, rho=.5, d=0.043, maturity=18, endrepro=65, population=testres$population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z),F_Th = 60)

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=5)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T,sizes=c(50,50))

communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))
initcomus$size=unname(table(smallpop[,"community"]))
multrep=replicate(10,modelVector(K=K, m=1, b=0.39, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize","popfull","repros","births"),logging=c("time","fission"),ma=1,traitsid=paste0("t",1:z),F_Th=180))


plot(quickV$popsize)
plot(quickV$births)
plot(quickV$deaths)
plot(quickV$repros/quickV$popsize[-1],type="l")
initcomus$occupation[,]=1
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(K*50,age="random",community = communities),initNeutralTraits(K*50,2))
newtestres=modelVector(K=K, m=1, b=0.5, r=0, rho=.5, d=0.03, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time"),ma=1,traitsid=paste0("t",1:2),F_Th = 55)

table(newtestres$population[,"community"])
population=newtestres$population

rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))

par(mfrow=c(3,2))
plot(1,1,main="population size",xlab="time",ylab="# number individual",log="y",ylim=c(1,5000),type="l",lwd=2,xlim=c(0,501))
for(repil in 1:ncol(multirep)) lines(multirep[,repil]$popsize,,main="#death vs popsize",col=repil,lwd=2)
plot(1,1,main="number of valid couple",type="l",log="y",lwd=2,ylim=c(1,2000),xlim=c(0,501))
for(repil in 1:ncol(multirep)) lines(multirep[,repil]$repro,main="number of valid couple",col=repil,type="l",lwd=2)
plot(1,1,xlab="population size",ylab="number of death",main="#death vs popsize",ylim=c(1,100),xlim=c(0,500))
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$deaths,xlab="population size",ylab="number of death",main="#death vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$births,xlab="population size",ylab="number of birth",main="#birth vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$repros,xlab="population size",ylab="number parents",main="#parents vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$repros,col=repil)
plot(newtestres$repros/newtestres$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,ylim=c(0,.5))
for(repil in 1:ncol(multirep)) 
lines(multirep[,repil]$repros/multirep[,repil]$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,col=repil)


bs=round(runif(100,.35,.41),digit=2)
devtools::load_all(".")
bs=round(runif(500,.34,.38),digit=3)
data(smallpop)
traitsid=paste0("t",1:4)
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=100,plot=T,sizes=50)
initcomus$size=unname(table(smallpop[,"community"]))
library(parallel)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsiz=parSapply(cl,bs,function(b){
           res=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=initNeutralTraitsPathways(z=4),age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100)$popsize
})
stopCluster(cl)
par(mfrow=c(1,3))
boxplot(lengths(allpopsiz)~bs,ylab="simu length vs birth rate ",xlab="birth rate",main="extinctions")
finished=allpopsiz[lengths(allpopsiz)==500]
finsize=sapply(finished,"[",500)
boxplot(finsize~bs[lengths(allpopsiz)==500],ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end without extinctions")
abline(h=nrow(smallpop),col="red")
boxplot(finsize~bs[lengths(allpopsiz)==500],ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",ylim=c(1,1500),log="y",main="pop at end without extinctions")

allfinal=sapply(allpopsiz,function(i)i[length(i)])
boxplot(allfinal~bs,ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end ")
abline(h=nrow(smallpop),col="red")


boxplot(log(allfinal+1))

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=ki,km=km,traits=a,coordinates=pos,G=100,plot=T,sizes=c(50))
initcomus$occupation[,]=1
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(K*percomu,age="random",community = communities),generateTraitsMatrix(K*50,2))
newtestres=modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time"),ma=1,traitsid=paste0("t",1:2),F_Th = 70)
table(newtestres$population[,"community"])
population=newtestres$population
rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))
population=resetIds(population)

traitsid=paste0("t",1:2)
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=10)
a=initAdaptiveTraits(ki=ki,km=km,n=3 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T)
initcomus$size=unname(table(population[,"community"]))
#initcomus$adaptivetraits[3,]=1
library(parallel)
population=cbind(population[,1:9],generateTraitsMatrix(nrow(population),24))
expname="NeutrEvoLSingleBR2kRHO_1_limited"
dir.create(expname)
traitsid=paste0("t",1:24)
population[,traitsid]=0
population[population[,"community"]==1,traitsid]=1
population[population[,"community"]==2,traitsid]=1
bs=round(runif(300,.338,.345),digit=4)
cl<-makeCluster(40,type="FORK",outfile=file.path(expname,"log.txt"))
allpopsizesonly=parSapply(cl,1:200,function(b){
                              set.seed(as.numeric(Sys.time())+b)
                              tryCatch({
           singlesimu=modelVector(K=K, m=1, b=0.348, r=0, rho=1, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=2000, tp=neutraltraitsParam,age.threshold=20, out=c("popsize","finalpop","finalcomus","traitsumary","popsumary","deaths","births","repros"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F)
           saveRDS(file=file.path(expname,paste0("singlesimu_s_",b,".RDS")),singlesimu)
           singlesimu$popsize
                              },error=function(e){ print("problem ======");print(e)})
})
stopCluster(cl)
saveRDS(file=file.path(expname,"neutralTraits_longer.RDS"),allpopsizesonly)

expname="AdapEvoLSingleBR5kRHO_1"
cl<-makeCluster(40,type="FORK",outfile=file.path(expname,"log.txt"))
initcomus$adaptivetraits[c(3,6),]=1
allpopsizesonly=parSapply(cl,1:80,function(b){
                              set.seed(as.numeric(Sys.time())+b)
                              tryCatch({
           singlesimu=modelVector(K=K, m=1, b=0.348, r=0.05, rho=1, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("popsize","finalpop","finalcomus","traitsumary","popsumary","deaths","births","repros"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F,beta=-1)
           saveRDS(file=file.path(expname,paste0("singlesimu_s_",b,".RDS")),singlesimu)
           singlesimu$popsize
                              },error=function(e){ print("problem ======");print(e)})
})
stopCluster(cl)
saveRDS(file=file.path(expname,"neutralTraits_longer.RDS"),allpopsizesonly)
expname="AdapEvoLSingleBR5kRHO_1_longer"
cl<-makeCluster(40,type="FORK",outfile=file.path(expname,"log.txt"))
allpopsizesonly2=parSapply(cl,1:200,function(b){
                              set.seed(as.numeric(Sys.time())+b)
                              tryCatch({
           singlesimu=modelVector(K=K, m=1, b=0.348, r=0.02, rho=1, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=2000, tp=neutraltraitsParam,age.threshold=20, out=c("popsize","finalpop","finalcomus","traitsumary","popsumary","deaths","births","repros"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F)
           saveRDS(file=file.path(expname,paste0("singlesimu_s_",b+80,".RDS")),singlesimu)
           singlesimu$popsize
                              },error=function(e){ print("problem ======");print(e)})
})
stopCluster(cl)
saveRDS(file=file.path(expname,"neutralTraits_longer2.RDS"),allpopsizesonly)
plot(allpopsiz[[1]],xlim=c(0,500),ylim=range(compressedts))
compressedts=sapply(1:500,function(t)sapply(allpopsizesonly[lengths(allpopsizesonly)>2],function(i)i[t]))
getdist=apply(compressedts,2,quantile,na.rm=T)

compressedts=sapply(1:500,function(t)sapply(allpopsiz,function(i)i[t]))

uniqutest=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=initNeutralTraitsPathways(z=2),age.threshold=20, out=c("popsize","births","deaths","repros","finalcomus","finalpop","popfull"),logging=c("done","time"),ma=1,traitsid=traitsid,F_Th=50,testdebug=F)

allpopu=sapply(uniqutest$popfull,function(population){
sapply(1:25,function(c){
           print(c)
           subpop=population[population[,"community"]==c,,drop=F]
           if(length(subpop)!=0){
               sum(validCouple(subpop,maturity=18,endrepro=65))
           }
           else
               NA
})
})
plot(1,1,type="n",ylim=c(0,1),xlim=c(0,500))
for(co in 1:25){
    lines(allpopu[co,],lwd=2,col=co)
}

allsize=sapply(uniqutest$popfull,function(population){
sapply(1:25,function(c){
           print(c)
           subpop=population[population[,"community"]==c,,drop=F]
           if(length(subpop)!=0){
           nrow(subpop)
           }
           else
               NA
})
})
simuresu=readRDS("fullout.RDS") 

repros=apply(sapply(1:500,function(t)apply(simuresu,2,function(i)i$repros[t])),2,quantile,na.rm=T)
popsizes=apply(sapply(1:500,function(t)apply(simuresu,2,function(i)i$popsize[t])),2,quantile,na.rm=T)
popsizes=apply(sapply(1:500,function(t)apply(simuresu,2,function(i)i$popsize[t])),2,quantile,na.rm=T)


allpopsiz=sapply(1:500,function(t)apply(simuresu,2,function(i)i$popsize[t]))
allrepros=sapply(1:500,function(t)apply(simuresu,2,function(i)i$repros[t]))
alldeaths=sapply(1:500,function(t)apply(simuresu,2,function(i)i$deaths[t]))
allbirths=sapply(1:500,function(t)apply(simuresu,2,function(i)i$births[t]))
deaths=apply(alldeaths,2,quantile,na.rm=T)
births=apply(allbirths,2,quantile,na.rm=T)
plot(allpopsiz,allrepros)
hist(allrepros/allpopsiz)
plot(popsizes[1,],deaths[1,])
points(popsizes[1,],deaths[1,])
abline(0,0.04,col="red")
plot(popsizes[3,],births[3,])
abline(0,0.04,col="red")
text(450,15,expression(y==0.04*x),col="red") 
library(parallel)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsiz=parSapply(cl,bs,function(b){
           res=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=paste0("t",1:z),F_Th=180)
           res$popsize[length(res$popsize)]
})
stopCluster(cl)
